\texttt{CompleteThat}: A python package for low-rank matrix completion\\EEOR E4650 Course Project

### 2015-01-06 document/article.tex
update document

	\item Step Size: The algorithms performance is highly dependent on the step size (alpha) parameter of the update equations. Too small of a alpha will result in convergence taking a very long time and lower the chance of finding the global objective. Too large of a alpha will result in convergence not happening as the the algorithm continually 'overshoots' the optimal value.

	\item Shuffle: When dealing with large data we need to be clever with how we shuffle our data. Shuffling is no trivial task out of memory. We explored several out of memory methods but ultimately decided with using a pseudo-shuffle, where we read in the file in large chunks that fit in memory, shuffle the lines using built in python functions, write the records back to a text file, and continue until the all of the file has been pseudo-shuffled. Hopefully by choosing a large enough batch size for reading in, our file is shuffle well enough. We also explored with a more robust method of shuffling the shuffled batches, but the added time complexity of appending large files together did not prove worthwhile given almost negligible returns in convergence.

>>>>

	\item Step Size: The algorithms performance is highly dependent on the step size ($\alpha$) parameter of the update equations. Too small of a alpha will result in convergence taking a very long time and lower the chance of finding the global objective. Too large of a alpha will result in convergence not happening as the the algorithm continually 'overshoots' the optimal value. Thus an essential part of using this algorithm will be experimentation with the step size. Currently, the step size (alpha parameter) is fully adjustable, with the default being a .01 decreasing 30\% each pass over the data until it reaches 1e-6 whereby it will remain constant until the stopping criterion of the algorithm are reached.

	\item Shuffle: When dealing with large data files we needed to be clever with how we shuffle our data. Stochastic gradient descent performs much better with shuffling of the data after each pass over the file thus shuffling is essential; yet shuffling is no trivial task for files too big to fit entirely into the computers random access memory. We explored various shuffling methods for both in-memory and out-of-memory but ultimately decided with using a batch pseudo-shuffle. Our batch shuffle method shuffles the file in chunks. So we read in some large portion (the batch size) of the file that will fit in memory, we shuffle the ratings of that batch using built in python functions, and lastly we write the shuffled ratings back to a text file, and continue sequentially until the all of the file has been shuffled. Following this method we say 'pseudo-shuffled' since the file is not truly shuffled. It is shuffled within the batch/portion of the file it belongs to but still not truly shuffled within the entire file. The larger the batches, the better the shuffled ratings, until of course we read the entire file into memory and shuffle it, the ideal situation. Hopefully by choosing a large enough batch size for reading in, our file will be shuffled well enough. We also explored a more robust method of shuffling the data by additionally shuffling the shuffled batches whereas before we wrote the shuffled ratings back to a file sequentially.  However ultimately the noticeably bigger time complexity of moving and appending large files together via Linux did not prove worthwhile given almost negligible returns in convergence
